Continuous developmental changes in word recognition across early childhood support early language learning

### 2025-02-04 paper/paper.Rmd
messing around with plotting

@@

graph_sem(model = fit3_age, text_size = 2, layout = t(layout_age))

nodes <- get_nodes(fit3_age)

edges <- get_edges(fit3_age) |> filter(label!="1.00") |>

graph_sem(edges=edges, nodes=nodes, text_size = 2, layout = t(layout_age),
          rect_width=2,
          rect_height=1.2,
          ellipses_width=1.5,
          ellipses_height=1.5,
          variance_diameter=.9,
          spacing_x=2
)
```

@@

```{r longitudinal, fig.env="figure*", height = 3.5, fig.cap = "Structural equation model showing longitudinal couplings between growth parameters. "}
#layout <- read.csv(here("misc/layout_slopes_observed_growth.csv"), header = FALSE)
#graph_sem(model = slopes_long, text_size = 2, layout=t(layout))
graph_sem(model = slopes_long, text_size = 2)

```

>>>>

source(here("helper/modified_sem_plot.R"))

@@

node_text <- tibble(name=c("acc", "acc_sd", "accuracy", "comp", "log_age", "log_rt", "log_rt_sd", "prod", "speed", "vocab"), pretty=c("Accuracy", "Accuracy (sd)", "Accuracy", "Comprehension", "Age (log months)", "log RT", "log RT (SD)", "Production", "Speed", "Vocabulary"))

nodes <- get_nodes(fit3_age) |> tibble() |> left_join(node_text) |> mutate(label=ifelse(shape=="oval",pretty, str_c(pretty, "\n", est_sig)))

edges <- get_edges(fit3_age) |> filter(label!="1.00") |> mutate(label_location=.5)

edges[17,"curvature"]=50
edges[17,"label_location"]=.6

source(here("helper/modified_sem_plot.R"))

#View(edges)
prepare_graph(edges=edges, nodes=nodes, text_size = 2.5, layout = t(layout_age),
          rect_width=4.2,
          rect_height=3,
          ellipses_width=3,
          ellipses_height=3,
          variance_diameter=2,
          spacing_y=4,
          spacing_x=4,
          fix_coord=FALSE) |> plot_happy_arrows()
```

@@

```{r longitudinal, fig.env="figure*", height = 3.5, fig.cap = "Structural equation model showing longitudinal couplings between growth parameters. "}
layout <- read.csv(here("misc/layout_slopes_observed_growth.csv"), header = FALSE)

node_text <- tribble(~name, ~ pretty,
                     "acc_t0", "t0 Accuracy",
                     "acc_t1", "t1 Accuracy",
                     "acc_t2", "t2 Accuracy",
                     "acc_t3", "t3 Accuracy",
                     "acc_t4", "t4 Accuracy",
                     "accuracy_intercept", "Accuracy intercept",
                     "accuracy_slope", "Accuracy slope",
                     "log_rt_t0", "t0 log RT",
                     "log_rt_t1", "t1 log RT",
                     "log_rt_t2", "t2 log RT",
                     "log_rt_t3", "t3 log RT",
                     "log_rt_t4", "t4 log RT",
                     "prod_t0" , "t0 Production",
                     "prod_t1" , "t1 Production",
                     "prod_t2" , "t2 Production" ,
                     "prod_t3", "t3 Production",         
                     "prod_t4", "t4 Production" ,
                     "speed_intercept" , "Speed intercept" ,  
                     "speed_slope" , "Speed slope",
                     "vocab_intercept", "Vocabulary intercept",
                     "vocab_slope", "Vocabulary slope" )

nodes <- get_nodes(slopes_long) |> tibble() |> left_join(node_text) |> mutate(label=pretty)

edges <- get_edges(slopes_long) |> mutate(label_location=.5) |> mutate(label=ifelse(arrow=="last", NA, label)) |>  mutate(connect_from=ifelse(to==from, "right",NA),
                    connect_to=connect_from) |> 
  mutate(color="black")

edges[52,"curvature"]=85
edges[52,"color"]="blue"
edges[61,"curvature"]=85
edges[61,"color"]="blue"
edges[66,"curvature"]=85
edges[66,"color"]="blue"

edges[54,"curvature"]=85
edges[63,"curvature"]=85

edges[53,"curvature"]=80
edges[53,"color"]="red"
edges[55,"curvature"]=82
edges[55,"color"]="red"
edges[62,"curvature"]=80
edges[62,"color"]="red"

edges[58,"curvature"]=80
edges[58,"color"]="green"
edges[60,"curvature"]=82
edges[60,"color"]="green"
edges[65,"curvature"]=80
edges[65,"color"]="green"

edges[59,"curvature"]=77

edges[64,"curvature"]=75
edges[56,"curvature"]=75
edges[57,"curvature"]=75

source(here("helper/modified_sem_plot.R"))
#View(edges)
prepare_graph(edges=edges, nodes=nodes, text_size = 2, layout = t(layout),angle=0,
          rect_width=1.5,
          rect_height=2,
          ellipses_width=1.5,
          ellipses_height=4,
          variance_diameter=1,
          spacing_y=3,
          spacing_x=2,
          fix_coord=FALSE) |> 
  edit_edges({connect_from=case_when(
    (to==from & from %in% c("accuracy_intercept","accuracy_slope","speed_slope",
                          "speed_intercept", "vocab_slope", "vocab_intercept"))~"bottom",
    to==from ~ "right",
    !is.na(curvature)~"left",
    T ~ "right")}) |> 
  plot_happy_arrows()
```
